Supplemental Materials for: Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-05-13 doc/peakcharacterization_supplemental.Rmd
included frequency models
close #31

>>>>

## Alternative Frequency Models

We can define several models, and test them on the four samples.

```{r increment_models}
figure_count$increment("frequency_models")
table_count$increment("frequency_models")
```

$$frequency = a + \frac{y}{\sqrt{mz}} (1)$$

$$frequency = a + \frac{x}{mz} + \frac{y}{\sqrt{mz}} (2)$$

$$frequency = a + \frac{x}{mz} + \frac{y}{\sqrt{mz}} + \frac{z}{\sqrt[3]{mz}} (3)$$

$$frequency = a + \frac{y}{\sqrt{mz}} + \frac{z}{\sqrt[3]{mz}} (4)$$

`r figure_count$label_text("frequency_models")` shows the median absolute deviation (MAD) and medians of the residuals between the calculated and predicted frequency values after fitting of frequency to m/z in each scan using each model, and then across each sample.
It is clear that model 3 that includes all three of the m/z terms performs the best in terms of overall fit, although there may be some disagreement between the ECF and lipid samples based on median of the residual differences.
`r table_count$label_text("frequency_models")` shows the coefficients for each term of the models for the 1ecf sample.
The coefficients of the **y** term in each of the models is orders of magnitude larger than the coefficients for any of the other terms in the other models.
That term also appears relatively constant, with some small variations to account for the presence and absence of the other terms of the model.

```{r load_model_results}
tar_load(frequency_1ecf)
tar_load(frequency_2ecf)
tar_load(frequency_49lipid)
tar_load(frequency_97lipid)

all_models = list(
  `1ecf` = frequency_1ecf,
  `2ecf` = frequency_2ecf,
  `49lipid` = frequency_49lipid,
  `97lipid` = frequency_97lipid
)

```

```{r frequency_models, dn_id = figure_count, fig.width = 8, fig.height = 9}
create_plot = function(in_sample){
  mad_plot = in_sample$mad_data %>%
    ggplot(aes(x = model, y = mad)) +
    geom_sina() +
    labs(x = "Frequency Model", y = "MAD(residuals)",
         subtitle = in_sample$sample)
  median_plot = in_sample$mad_data %>%
    ggplot(aes(x = model, y = median)) +
    geom_sina() +
    labs(x = "Frequency Model", y = "Median(residuals)")
  mad_plot | median_plot
}
sample_plots = purrr::map(all_models, create_plot)

wrapped_plots = wrap_plots(sample_plots, ncol = 1)
wrapped_plots
```

`r figure_count$label_text("frequency_models")`.
Sina plots of the median absolute deviation (MAD) and median of the residuals between the calculated frequency using the m/z spacing and the predicted frequency after fitting a frequency model, for each of the four samples and for each of the models (1 - 4) defined above.

`r table_count$label_text("frequency_models")`.
Coefficients for each term in the models after fitting of the calculated frequency to m/z.

```{r coefficient_table}
ecf_coef_table = all_models[[1]]$model_data %>%
  flextable() %>%
  colformat_double(digits = 0) %>%
  autofit()
ecf_coef_table
```
